---
title: "CapstoneHG"
author: "SarahCannon"
date: "June 24, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("P:/Capstone")

#install.packages("tidytext")
library(tidytext)

#install.packages("pdftools")
library(pdftools)

#install.packages("stringr")
library(stringr)

#install.packages("DMwR")
library(DMwR)

install.packages("e1071")
library(e1071)

library(dplyr)
library(tidyr)

```

#Pard D of Oakville's Official Plan contains land use permissions.

```{r}
download.file("https://www.oakville.ca/assets/2011%20planning/Part%20D%2004-04-2017.pdf", "Part%20D%2004-04-2017.pdf")
partd <- pdf_text("Part%20D%2004-04-2017.pdf")

pd <- strsplit(partd, "\n")

head(pd)

pdun <- data.frame(unlist(pd, recursive = TRUE))

colnames(pdun) <- "pdoptext"

pdun$pdoptext <- as.character(pdun$pdoptext)

pdun$dhf <- ifelse(startsWith(pdun$pdoptext, "Livable"), "hf", "")
pdun$dhf <- ifelse(startsWith(pdun$pdoptext, "D-"), "hf", pdun$dhf)
pdun$dhf <- ifelse(startsWith(pdun$pdoptext, "Last"), "hf", pdun$dhf)
pdun$dhf <- ifelse(startsWith(pdun$pdoptext, "Part D:"), "hf", pdun$dhf)
pdun$dhf <- ifelse(endsWith(pdun$pdoptext, "blank."), "hf", pdun$dhf)

pdun$dpol <- as.numeric(grepl("^[0-9]", pdun$pdoptext))

pdun$dsec <- ifelse(pdun$dpol == 1, word(pdun$pdoptext), '')

secnum <- "11."
rw <- 1

for (rw in c(1:length(pdun$dsec))) {
  if (pdun$dsec[rw] == '') {
    pdun$dsec[rw] <- secnum
    rw == rw + 1
  } else {
    secnum <- pdun$dsec[rw]
    rw == rw + 1
  }
}
```

#And now, tidytext

```{r}
#let's use unnest tokens because it's tibble time, y'all
peuntib <- peun %>% unnest_tokens(word, optext)

#remove stop words
data("stop_words")

peuntib <- peuntib %>% anti_join(stop_words)

peuntibct <- peuntib %>% group_by(sec) %>% count(word, sort = TRUE)


```

#Now for Part D tibble time...

```{r}
#let's use unnest tokens because it's tibble time, y'all
pduntib <- pdun %>% unnest_tokens(word, pdoptext)

#remove stop words
data("stop_words")

pduntib <- pduntib %>% anti_join(stop_words)

pduntibct <- pduntib %>% group_by(dsec) %>% count(word, sort = TRUE)
```

#Find key words and merge - this will indicate

```{r}
#Make subsets of records with the keywords
ptcd_units <- subset(pduntibct, pduntibct$word == "units")
ptcd_dir <- subset(pduntibct, pduntibct$word == "directed")
ptcd_number <- subset(pduntibct, grepl("^[0-9]", pduntibct$word))
ptcd_max <- subset(pduntibct, pduntibct$word == "maximum")
ptcd_min <- subset(pduntibct, pduntibct$word == "minimum")
ptcd_storeys <- subset(pduntibct, pduntibct$word == "storeys")
ptcd_puse <- subset(pduntibct, pduntibct$word == "permitted")
ptcd_pro <- subset(pduntibct, pduntibct$word == "prohibited")


colnames(ptcd_units) <- c("usec", "uword", "un")
colnames(ptcd_dir) <- c("dirsec", "dword", "dn")
colnames(ptcd_number) <- c("nsec", "nword", "nn")
colnames(ptcd_max) <- c("maxsec", "maxword", "maxn")
colnames(ptcd_min) <- c("minsec", "minword", "minn")
colnames(ptcd_storeys) <- c("ssec", "sword", "sevn")
colnames(ptcd_puse) <- c("psec", "pword", "pn")
colnames(ptcd_pro) <- c("prosec", "proword", "pron")

#ptc_number needs some editing because it's the only case where there can be multiple entries (aka numbers) per policy...
ptcd_number <- subset(ptcd_number, ptcd_number$nsec != ptcd_number$nword)
ptcd_number <- ptcd_number %>% group_by(nsec) %>% summarise(nword = n_distinct(nword))

#Make a master list of all sections
Dsec <- data.frame(unique(pdun$dsec))
colnames(Dsec) <- c("dsec")

#Merge the keywords
dm1 <- merge(Dsec, ptcd_units, by.x = "dsec", by.y = "usec", all.x = TRUE)
dm2 <- merge(dm1, ptcd_dir, by.x = "dsec", by.y = "dirsec", all.x = TRUE)
dm3 <- merge(dm2, ptcd_number, by.x = "dsec", by.y = "nsec", all.x = TRUE)
dm4 <- merge(dm3, ptcd_max, by.x = "dsec", by.y = "maxsec", all.x = TRUE)
dm5 <- merge(dm4, ptcd_min, by.x = "dsec", by.y = "minsec", all.x = TRUE)
dm6 <- merge(dm5, ptcd_storeys, by.x = "dsec", by.y = "ssec", all.x = TRUE)
dm7 <- merge(dm6, ptcd_puse, by.x = "dsec", by.y = "psec", all.x = TRUE)
kwdsec <- merge(dm7, ptcd_pro, by.x = "dsec", by.y = "prosec", all.x = TRUE) 

#Add columns to store relevant info
kwdsec$kwct <- rowSums(kwdsec[,c(3,5,6,8,10,12,14,16)], na.rm = TRUE)
```

#Looking at bps

```{r}
bpza <- read.csv("P:/Capstone/bpza.csv", stringsAsFactors = FALSE)

bpza$type <- ifelse(startsWith(bpza$FOLDERTYPE, "Residential"), "Res", "")
bpza$type <- ifelse(startsWith(bpza$FOLDERTYPE, "Commercial"), "Com", bpza$type)
bpza$type <- ifelse(startsWith(bpza$FOLDERTYPE, "Industrial"), "Ind", bpza$type)
bpza$type <- ifelse(startsWith(bpza$FOLDERTYPE, "Institutional"), "Inst", bpza$type)
bpza$type <- ifelse(startsWith(bpza$FOLDERTYPE, "Demolition"), "Dem", bpza$type)
bpza$type <- ifelse(startsWith(bpza$FOLDERTYPE, "Fire"), "Fire", bpza$type)
bpza$type <- ifelse(startsWith(bpza$FOLDERTYPE, "Plumbing"), "Plu", bpza$type)
bpza$type <- ifelse(startsWith(bpza$FOLDERTYPE, "Town"), "Res", bpza$type)
bpza$type <- ifelse(startsWith(bpza$FOLDERTYPE, "Tent"), "Misc", bpza$type)
bpza$type <- ifelse(startsWith(bpza$FOLDERTYPE, "Miscellaneous"), "Misc", bpza$type)
bpza$type <- ifelse(startsWith(bpza$FOLDERTYPE, "Accessory"), "Res", bpza$type)


```

#Focus on residential

```{r}
resbpza <- subset(bpza, bpza$type == "Res" & bpza$CLASS != "")
resbp <- resbpza[,c(2,3,4,5,6,9,23,30,34)]

#collapsing class - consider res and no res
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Residential Low"), "reslow", "")
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Residential Medium"), "resmed", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Residential High"), "reshigh", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Residential Uptown"), "resutc", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Central Business"), "nres", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Main"), "nres", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Urban Core"), "nres", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Urban Centre"), "nres", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Park"), "nres", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Natural"), "nres", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Instituational"), "nres", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Community"), "nres", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Parkway"), "nres", resbp$clcol)
resbp$clcol <- ifelse(startsWith(resbp$CLASS, "Existing"), "nres", resbp$clcol)

```

#Get res building types and growth area; exclude "other" permits

```{r}
#res dwelling types
resbp$dwtype <- ifelse(startsWith(resbp$DESCRIPTIO, "Single"), "low", "")
resbp$dwtype <- ifelse(startsWith(resbp$DESCRIPTIO, "Semi"), "low", resbp$dwtype)
resbp$dwtype <- ifelse(startsWith(resbp$DESCRIPTIO, "Row"), "med", resbp$dwtype)
resbp$dwtype <- ifelse(endsWith(resbp$DESCRIPTIO, "Apartment"), "high", resbp$dwtype)
resbp$dwtype <- ifelse(resbp$dwtype == "", "other", resbp$dwtype)

#Growth area yes or no
resbp$ga <- ifelse(resbp$GROWTH_ARE == "", "no", "yes")

#Exclude permits that fall into the "other" category
resbp <- subset(resbp, !(resbp$dwtype == "other"))

```

#calculate what makes a good permit

```{r}
#If the building dwelling type corresponds to the OP, we're good, otherwise, we're not
resbp$align <- 0
resbp$align[resbp$clcol == "reslow" & resbp$dwtype == "low"] <- 1
resbp$align[resbp$clcol == "resmed" & resbp$dwtype == "med"] <- 1
resbp$align[resbp$clcol == "reshigh" & resbp$dwtype == "high"] <- 1

#Let's look at that class attribute balance:
table(resbp$align)
#eek!

```

#SMOTE to the rescue!!!

```{r}
#Create a new dataset with more balanced classes
#Make the class attribute a factor
resbp$align <- as.factor(resbp$align)

#only have relevant columns
resbpmod <- resbp[,c(10:13)]

#Make everything a factor!
resbpmod[,1] <- as.factor(resbpmod[,1])
resbpmod[,2] <- as.factor(resbpmod[,2])
resbpmod[,3] <- as.factor(resbpmod[,3])

bal_resbpmod <- SMOTE(align ~ ., resbpmod, perc.over = 700, k = 3, perc.under = 100)
table(bal_resbpmod$align)

```

#Now that we've smoted we can logistic regression!!!

```{r}
bpmodel <- glm(align ~ dwtype + clcol + ga, data = bal_resbpmod, family = "binomial")
summary(bpmodel)

predbp <- predict(bpmodel, type = 'response')
table(bal_resbpmod$align, predbp > 0.5)

bp_precision <- 595 / (595+181)
bp_recall <- 595 / (595 +23)
bp_F1 <- 2*((bp_precision * bp_recall)/(bp_precision + bp_recall))

results <- c(bp_precision, bp_recall, bp_F1)
results

#Not bad!!!

```

#Now that we've logistic regressioned we can naive bayes!

```{r}
bpmodelnb <- naiveBayes(align ~ dwtype + clcol + ga, data = bal_resbpmod)
bpmodelnb

predbpnb <- predict(bpmodelnb, bal_resbpmod)

table(predbpnb, bal_resbpmod$align)

bpnb_precision <- 618 / (618+190)
bpnb_recall <- 618 / (618+158)
bpnb_F1 <- 2*((bpnb_precision * bpnb_recall)/(bpnb_precision + bpnb_recall))
resultsnb <- c(bpnb_precision, bpnb_recall, bpnb_F1)
resultsnb

```

